Hydras \& Co.

### 2022-05-06 doc/gaia-chapter.tex
fix an error in latex doc

\subsubsection{Order and comparison}
\label{sect:lt-compat-gaia}
The  strict order on both types \texttt{T1} are
compatible:

\inputsnippets{T1Bridge/eqRef}
Note that \HydrasLib' comparison on ordinal terms uses a
\stdpp-like trichotomy, hence the first two lemmas below:

>>>>

\subsubsection{Order and comparison}
\label{sect:lt-compat-gaia}

The  strict orders on types \texttt{T1} and \texttt{hT1} are
compatible.
Note that \HydrasLib' comparison on ordinal terms uses a
\stdpp-like trichotomy, hence the first two lemmas below:
